References

### 2015-03-31 cv/XieXiaolei-Analyst.tex

% \section*{My Goal}
% A PhD student of Finance \& Insurance Mathematics at Copenhagen
% University, who is very experienced in programming and statistical
% analysis,
% % is looking for a part-time job as a quantitative analyst.
% is looking for a summer internship as a quantitative analyst.

@@

      I am also interested in efficient simulation of multivariate
      GARCH structures, which, among others, helps the determination of
      model parameters when fitting such a model to a large
      multi-dimensional data set.
  \end{itemize}

>>>>

\section*{My Goal}
% A PhD student of Finance \& Insurance Mathematics at Copenhagen
A PhD of Finance \& Insurance Mathematics at Copenhagen
University, who is very experienced in programming and statistical
analysis,
% is looking for a part-time job as a quantitative analyst.
% is looking for a summer internship as a quantitative analyst.
is looking for a role of quantitative analysis.

@@

      I am also interested in efficient simulation of multivariate
      GARCH structures, which, among others, helps the determination of
      model parameters when fitting such a model to a large
      multi-dimensional data set.

      \item{\it Teaching:} I teach exercise classes of the
        master-level course ``Statistical Methods of Non-life
        insurance'', which includes Maximum-likelihood estimators,
        hypothesis testing and linear regression, among others. I
        first solve the problems myself and then present and explain the
        solutions to the class upon the students' request.

  \end{itemize}
